Finite-state morphological transducers for three Kypchak languages

### 2014-02-16 kipchak-lrec-2013/kipchak-paper.tex
update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@50293 72bbbca6-d526-0410-a7d9-f06f51895060

\subsection{Kumyk}
Kumyk /qumuq/ is spoken in Dagestan, a Republic of the Russia Federation, where it is co-official with a number of other languages of Dagestan \citep{ethnologue}.  There are approximately 430 thousand speakers \citep{ethnologue}.

>>>>

\subsection{Kumyk}
Kumyk /qumuq/ is spoken in Dagestan, a Republic of the Russian Federation, where it is co-official with a number of other languages of Dagestan \citep{ethnologue}.  There are approximately 430 thousand speakers \citep{ethnologue}.
